---
title: "Goose model testing"
author: "The awesome Goose management Team"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, cache=FALSE, tidy=FALSE,echo=FALSE}
assign("depthtrigger", 60, data.table:::.global)  # To prevent data.table printing when removing columns. See: http://stackoverflow.com/questions/15267018/knitr-gets-tricked-by-data-table-assignment
```


```{r load, echo=FALSE,message=FALSE, warning=FALSE, include=FALSE}
# library(devtools)
# install_github('LDalby/ralmass') 
packs = c('xtable', 'RColorBrewer', 'ralmass', 'gridExtra', 'knitr', 'lubridate', 'viridis', 'tidyverse', 'data.table', 'stringr', 'readxl', 'ggvis')
sapply(packs, FUN = require, character.only = TRUE)
runinfo = readLines('c:/MSV/WorkDirectory/BatchALMaSS.ini')
simyears = as.numeric(runinfo[length(runinfo)-1])

extention = ''

resultpath = 'c:/MSV/WorkDirectory/'

sim = ''
extention = '.res'

```

This is a workdocument for collecting output from the **ALMaSS** Goose management model.

Document compiled: `r Sys.time()`

Number of simulation years: `r simyears` (only valid for commandline runs)

Results read from: `r resultpath`

Date stamp on ALMaSS exe file: `r file.info(paste0(resultpath, 'ALMaSS_CmdLine.exe'))$mtime` 

## Notes to run
`r Sys.Date()`. Things modified:

+ See the config table below for the settings used for the goose model. 
+ Testing new logic in the followinglikelyhood code.

## Available forage
```{r forage, echo=FALSE, fig.width=14, fig.height=16, warning=FALSE}
coltypes = "iiiiiiiiiiiidddddcddicc"
forage = read_tsv(file.path(resultpath, 'GooseFieldForageData.txt'), col_types = coltypes) %>% 
  mutate(Day = Day-365, Date = as.Date(Day, origin = as.Date('2009-01-01'))) %>% 
  filter(month(Date) %in% c(8:12,1:2), Geese > 0) %>% 
  ClassifyHabitatUse(species = 'goose')

# First melt the numbers:
numbers_tb = forage %>%
  select(Day, Polyref, Grain, Maize, Barnacle, Pinkfoot, Greylag) %>% 
  gather_(key_col = "Species", value_col = "Number", gather_cols = c("Barnacle", "Pinkfoot", "Greylag"))
  
# Then melt the grass forage
grassforage_tb = forage %>%
  select(Day, Polyref, GrassPinkfoot, GrassBarnacle, GrassBarnacle) %>% 
  gather_(key_col = "Species", value_col = "KjAvailable", gather_cols = c("GrassPinkfoot", "GrassBarnacle", "GrassBarnacle")) %>% 
  mutate(Species = str_sub(Species, start = 6))

# Then merge and plot
left_join(numbers_tb, grassforage_tb, by = c('Day', 'Polyref', 'Species')) %>% 
  rename(Grass = KjAvailable) %>% 
  gather_(key_col = "Type", value_col = "KjAvailable", gather_cols = c('Grain', 'Maize', 'Grass')) %>% 
  filter(Number > 0, KjAvailable > 0.01) %>% 
  ggplot(aes(Day, KjAvailable)) + geom_point(alpha = 1/10, aes(size = log10(Number))) +
  facet_grid(Type~Species, scales = 'free_y') + theme_bw()
```
Plot characters and lines all have the same grey color, so black chunks are the result of overplotting. Only fields where the geese where actually foraging on are plotted. Dots are scaled to the logarithm of the numbers present on a field.
Turn off this chunk to save time when the document complies.


## Weight development
```{r weight, echo=FALSE, fig.width=10, message=FALSE, warning=FALSE}
weights = fread(file.path(resultpath, 'GooseWeightStats.txt'), showProgress = FALSE) %>% 
    filter(MeanWeight != -1) %>% 
    mutate(Day = Day-365,
           Date = as.Date(Day, origin = as.Date('2009-01-01')),
           SEupper = MeanWeight+StdError,
           SElower = MeanWeight-StdError)

weights %>% ggplot(aes(Date, MeanWeight)) +
      geom_point() +
      geom_errorbar(aes(ymin = SElower, ymax = SEupper), width = 0.5) + 
      facet_wrap(~Species, scales = 'free_y')

field = fread('C:/MSV/ALMaSS_inputs/GooseManagement/Vejlerne/APIdata.txt')
fits = CalcWeightFit(weights, field, measure = 'LS')
```

Fit(s) were `r fits`.

## Distance flown
```{r flightdistance, echo=FALSE, fig.height=6, fig.width=10}
massdropcols = c("BodyCondition", "MinForageRate")
energy <- fread(file.path(resultpath, 'GooseEnergeticsData.txt'), showProgress = FALSE, drop = massdropcols) %>% 
  as.tibble() %>% 
  mutate(Day = Day-365,
         Date = as.Date(Day, origin = as.Date('2009-01-01'))) %>% 
  group_by(Day, GooseType) %>% 
  mutate(MeanDist = mean(FlightDistance)/1000)
energy %>% select(Day, Date, GooseType, MeanDist, Season) %>% 
  distinct(.keep_all = TRUE) %>% 
  ggplot(aes(Date, MeanDist)) +
    geom_line(aes(color = GooseType)) +
    ylab('Mean distance flown per day (km)') +
    scale_color_brewer(palette = 'Paired') +
    scale_x_date(date_breaks = "1 month", date_labels = "%b") + 
    facet_wrap(~Season, scales = 'free_x')
```

## Full time
```{r fulltime, echo=FALSE, fig.height=5, fig.width=10}
energy %>% ggplot( aes(Day, FullTime)) +
  geom_hex(show.legend = TRUE) +
  scale_fill_viridis() +
  facet_grid(~GooseType)
```


## Number of flocks per day

```{r flocknumbers, echo=FALSE, fig.width=10}
forage %>%
  select(Day, GreylagTimed, BarnacleTimed, PinkfootTimed, Season) %>%
  gather_(value_col = 'Numbers', key_col = 'Species', gather_cols = c("GreylagTimed", "BarnacleTimed", "PinkfootTimed")) %>%
  filter(Numbers > 0) %>%
  group_by(Day, Species) %>%
  mutate(N = n()) %>% 
  ggplot(aes(Day, N)) +
  geom_line() +
  facet_wrap(~Species, scales = 'free') +
  ylab('Flock numbers')
```


## Numbers
```{r numbers, echo=FALSE, fig.height=6, fig.width=10}
invisible({ popn = fread(file.path(resultpath, 'GoosePopulationData.txt'))
popn[, Day:=Day-365] })
#popn = SubsetOutput(popn, CutOff) 
PlotGoosePopulation(data = popn, dates = TRUE)
```
\newpage

## Leave reason
```{r leavereason, echo=FALSE, fig.height=8, fig.width=10}
leavereason = read_tsv(file.path(resultpath, 'GooseLeaveReasonStats.txt'), col_types = "iiicci") %>% 
  filter(N > 0, Day = Day-365)
if(nrow(leavereason) > 0){
  ggplot(leavereason, aes(Day, N)) + 
    geom_line(aes(color = LeaveReason)) + 
    facet_grid(LeaveReason~SpeciesType, scales = 'free_y')
}
```

## Flock sizes
```{r flocks, echo=FALSE, fig.height=8, fig.width=10}
# Define helper function:
switch_names <-function(x) {
  switch(EXPR = x,
         "BarnacleTimed" = "Barnacle",
         "PinkfootTimed" = "Pinkfoot",
         "GreylagTimed" = "Greylag")
}


flocks <- read_csv('o:/ST_GooseProject/Field data/Fugledata/fugledata_20150320_obs_clean.csv') %>% 
  filter(Month %in% c(12,1) & Hour >= 11 & Hour <= 13) %>% 
  select(-Month, -Hour)

# Simulated data - max number on day
dists <- forage %>% 
  select(Day, Barnacle, Pinkfoot, Greylag) %>% 
  mutate(ObsDato = as.Date(Day, origin = '2014-01-01')) %>% 
  filter(month(ObsDato) %in% c(12,1)) %>% 
  select(-Day) %>% 
  gather_(key_col = 'Species', value_col = 'Numbers', gather_cols = c("Barnacle", "Pinkfoot", "Greylag")) %>% 
  filter(Numbers != 0) %>% 
  select(-ObsDato) %>% 
  mutate(Type = "Simulated") %>% 
  bind_rows(flocks) %>% 
  mutate(Numbers = log10(Numbers), Count = "DailyMax")

DegreeOverlapB = round(CalcOverlap(dists, species = 'Barnacle', metric = 'Numbers'), digits = 2)
DegreeOverlapP = round(CalcOverlap(dists, species = 'Pinkfoot', metric = 'Numbers'), digits = 2)
DegreeOverlapG = round(CalcOverlap(dists, species = 'Greylag', metric = 'Numbers'), digits = 2)

# Timed counts:
dists1 <- forage %>% 
  select(Day, BarnacleTimed, PinkfootTimed, GreylagTimed) %>% 
  mutate(ObsDato = as.Date(Day, origin = '2014-01-01')) %>% 
  filter(month(ObsDato) %in% c(12,1)) %>% 
  select(-Day) %>% 
  gather_(key_col = 'Species', value_col = 'Numbers', gather_cols = c("BarnacleTimed", "PinkfootTimed", "GreylagTimed")) %>% 
  filter(Numbers != 0) %>% 
  select(-ObsDato) %>% 
  mutate(Type = "Simulated") %>% 
  mutate(Species = map_chr(Species, .f = switch_names)) %>% 
  bind_rows(flocks) %>% 
  mutate(Numbers = log10(Numbers), Count = "Timed")

DegreeOverlapBT = round(CalcOverlap(dists1, species = 'Barnacle', metric = 'Numbers'), digits = 2)
DegreeOverlapPT = round(CalcOverlap(dists1, species = 'Pinkfoot', metric = 'Numbers'), digits = 2)
DegreeOverlapGT = round(CalcOverlap(dists1, species = 'Greylag', metric = 'Numbers'), digits = 2)

bind_rows(dists, dists1) %>% 
  ggplot(aes(x = Numbers, fill = Type)) +
  geom_density(alpha = 0.5, colour = NA) +
  facet_grid(Count ~ Species, scales = 'free_x') +
  theme_bw()
```

The degree of overlap is: Barnacle `r DegreeOverlapB`, Pinkfoot `r DegreeOverlapP`, & Greylag `r DegreeOverlapG`. For the timed counts the degree of overlap is: Barnacle `r DegreeOverlapBT`, Pinkfoot `r DegreeOverlapPT`, & Greylag `r DegreeOverlapGT`.

## Distance from foraging sites to nearest roost
```{r distances, echo=FALSE, fig.height=6, fig.width=12, message=FALSE}
# Data was handled here:
# polys = read_excel('o:/ST_GooseProject/Field data/Fugledata_Obslist_20160414_clean.xlsx', sheet = 'Polygon')
# polys = as.data.table(polys)
# obs = read_excel('o:/ST_GooseProject/Field data/Fugledata_Obslist_20160414_clean.xlsx', sheet = 'Observation')
# obs = as.data.table(obs)
# obs = obs[Year == 2015 & Month %in% c(9,10,11,12,1,2,3),]
# spIDs = c(63, 59, 67)
# spNames = c('Pinkfoot', 'Greylag', 'Barnacle')
# TheList = vector('list', length(spNames))
# for (i in seq_along(spIDs)) {
# 	observations = obs[ArtID == spIDs[i],]  # Subset to species
# 	polygons = polys[PolyID %in% observations$PolygonID,]  # Only get those polygons where the species were observed
# 	centroids = CalcPseudoCentroid(data = polygons, project = TRUE)  # Estimate the centroids
# 	temp = UtmToALMaSS(data = centroids, long = 'UtmX', lat = 'UtmY', map = 'VejlerneBigMap', subset = TRUE)
# 	temp[, Species:=spNames[i]]
# 	TheList[[i]] = temp
# }
# convertedobs = rbindlist(TheList)
# write.table(convertedobs, file = paste0('o:/ST_GooseProject/Field data/FieldobsDistancesFromRoost', Sys.Date(), '.txt'), row.names = FALSE, quote = FALSE)
col_types <- "iidiiiiii"
poly <- read_tsv(paste0(resultpath, 'Vejlerne2015_polyrefs_RenumFBHBOp.txt'), skip = 1, col_types = col_types)
col_types_field <- "iddddiic"
fieldobs <- read_delim('o:/ST_GooseProject/Field data/FieldobsDistancesFromRoost2016-04-25.txt', delim = ' ', col_types = col_types_field)
roost = read_tsv(paste0(resultpath,'GooseRoosts.txt'), skip = 1, col_names = FALSE, col_types = "iii")

DistToNearestRoostSim <- CalcDistToRoosts(roost = roost,
                                          fields = forage,
                                          polyref = poly,
                                          species = c('Pinkfoot', 'Barnacle', 'Greylag'),
                                          fieldobs = FALSE) %>% 
                          mutate(Type = "Simulated") %>% 
                          select(Shortest, Species, Type)

DistToNearestRoostField <- CalcDistToRoosts(roost = roost,
                                            fields = fieldobs,
                                            polyref = poly,
                                            species = c('Pinkfoot', 'Barnacle', 'Greylag'),
                                            fieldobs = TRUE) %>% 
                          mutate(Type = "Fieldobs") %>% 
                          select(Shortest, Species, Type)

distances <- bind_rows(DistToNearestRoostSim, DistToNearestRoostField)

RoostDistFitGL <- CalcOverlap(distances, species = 'Greylag', metric = 'Shortest')
RoostDistFitPF <- CalcOverlap(distances, species = 'Pinkfoot', metric = 'Shortest')
RoostDistFitBN <- CalcOverlap(distances, species = 'Barnacle', metric = 'Shortest')

# ggplot(Dists, aes(x=Shortest)) + geom_histogram(binwidth = 1000) + theme_bw() + facet_wrap(~Species)
# png(file = 'o:/ST_Lada/Projekter/GBB/Figures/DistanceToRoost.png', height = 480*2.5, width = 480*4, res = 400)
ggplot(distances, aes(x = log10(Shortest), fill = Type)) +
  geom_density(alpha = 0.5, colour = NA) +
  facet_wrap(~Species, scales = 'free_x') +
  theme_bw()
# dev.off()
``` 
The degree of overlap is: Barnacle `r RoostDistFitBN`, Pinkfoot `r RoostDistFitPF`, & Greylag `r RoostDistFitGL`.


## Habitat use
```{r habitat, habitatuse, echo=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
invisible({
FieldData = fread('o:/ST_GooseProject/Field data/Fugledata/HabitatUseAll2014.csv')
# habuse[, N:=sum(N), by=.(Month, HabitatUse, Species)]
FieldData[HabitatUse == 'Stubble undersown', HabitatUse:='Stubble']
FieldData[HabitatUse == 'UnharvestedBarley', HabitatUse:='Stubble']
FieldData = FieldData[HabitatUse != 'Plowed',]
FieldData[, NMTotal:=sum(N), by=.(Month, Species)]
FieldData[, Prop:=N/NMTotal]

forage[, Month:=month(as.Date(Day, origin = '2012-01-01'))]
HabitatUseFit = CalcHabitatUseFit(FieldData = FieldData, SimData = forage, measure = 'LS')
HabitatUseFit = CalcHabitatUseFit(FieldData = FieldData, SimData = forage, measure = 'SSSE')
HabUsePF = HabitatUseFit[Species == 'Pinkfoot', Fit]
HabUseGL = HabitatUseFit[Species == 'Greylag', Fit]
HabUseBN = HabitatUseFit[Species == 'Barnacle', Fit]
	
hbpf = forage[Month > 8 | Month == 1, .(PinkfootTimed, HabitatUsePF, Month)]
hbpf[, Species:='Pinkfoot']
hbpf = hbpf[complete.cases(hbpf),]
setnames(hbpf, old = c('HabitatUsePF', 'PinkfootTimed'), new = c('HabitatUse', 'N'))

hbgl = forage[Month > 8 | Month == 1, .(GreylagTimed, HabitatUseGL, Month)]
hbgl[, Species:='Greylag']
hbgl = hbgl[complete.cases(hbgl),]
setnames(hbgl, old = c('HabitatUseGL', 'GreylagTimed'), new = c('HabitatUse', 'N'))

hbbn = forage[Month > 8 | Month == 1, .(BarnacleTimed, HabitatUseBN, Month)]
hbbn[, Species:='Barnacle']
hbbn = hbbn[complete.cases(hbbn),]
setnames(hbbn, old = c('HabitatUseBN', 'BarnacleTimed'), new = c('HabitatUse', 'N'))
hb = rbind(hbpf, hbbn, hbgl)
setkeyv(hb, c('Species', 'Month'))

hb[,NMTotal:=sum(N), by=.(Month, Species)]
hb[, Prop:=N/NMTotal]
hb[, Month:=as.factor(Month)]
setkeyv(hb, c('Species', 'Month'))

FieldData[, Type:='FieldObs']
FieldData = FieldData[rep(seq(.N),N), .(Month, HabitatUse, N, Species, NMTotal, Prop, Type), by = Species]
hb[, Type:='Simulated']
SimData = hb[rep(seq(.N),N), .(Month, HabitatUse, N, Species, NMTotal, Prop, Type), by = Species]
dt = rbind(FieldData, SimData)
})
# png(file = 'o:/ST_Lada/Projekter/GBB/Figures/HabitatUse.png', height = 480*3.5, width = 480*4, res = 400)
ggplot(dt, aes(Month, fill = HabitatUse)) + geom_bar(position = 'fill') + theme_bw() +
 facet_grid(Type~Species) + scale_fill_brewer(palette = "Set2")
# dev.off()

# DK version:
# str(dt)
# dt[, Type:=as.factor(Type)]
# levels(dt$Type) = c('Feltobs', 'Simuleret')
# dt[, HabitatUse:=as.factor(HabitatUse)]
# levels(dt$HabitatUse) = c('Græs', 'Majs', 'Raps', 'Stub', 'Vintersæd')
# dt[, Species:=as.factor(Species)]
# levels(dt$Species) = c('Bramgås', 'Grågås', 'Kortnæbbet')
# 
# ggplot(dt, aes(Month, fill = HabitatUse)) + geom_bar(position = 'fill') + theme_bw() +
#  facet_grid(Type~Species) + scale_fill_brewer(palette = "Set2", guide = guide_legend(title = "Habitat")) + xlab('Måned') + ylab('Andel')



```
Habitat use fits were: Barnacle `r HabUseBN`, Greylag `r HabUseGL` & Pinkfoot `r HabUsePF`

## Huntingbag
```{r HuntingBag, eval=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
bag = fread('o:/ST_GooseProject/ALMaSS/HunterModelTesting/SurveyResults/THS_JAM_Goosehunters_2013.csv')
bag = bag[!is.na(ABMhunter),.(ABMhunter, Greylag, Pinkfeet)]
setnames(bag, old = 'Pinkfeet', new = 'Pinkfoot')
bag = melt(bag, id.vars = 'ABMhunter', measure.vars = c('Greylag', 'Pinkfoot'), variable.name = 'Species', value.name = 'NoShot')
bag[, Type:='Fieldobs']
	
simbag = fread('c:/MSV/WorkDirectory/HuntingBagRecord.txt')
if(nrow(simbag) != 0){ 
  simbag[, Species:=sapply(GameType, ConvertGameType)]
  simbag[, NoShot:=.N, by = c('Species', 'HunterRef')]
  sim = unique(simbag[, .(HunterRef, Species, NoShot)])
  sim[, Type:='Simulated']
  full = rbind(bag[NoShot != 0, .(Species, NoShot, Type)], sim[, .(Species, NoShot, Type)])
  full[, TotalBag:=sum(NoShot), by = c('Species', 'Type')]
  
  GLBagOverlap = CalcOverlap(data = full, species = 'Greylag', metric = 'NoShot')
  PFBagOverlap = CalcOverlap(data = full, species = 'Pinkfoot', metric = 'NoShot')

  cols = c('Fieldobs' = brewer.pal(8,'Dark2')[4], 'Simulated' = brewer.pal(8,'Dark2')[5])
  ggplot(full, aes(NoShot, fill = Type)) + geom_density(alpha = 0.5, colour = NA) + scale_fill_manual(values = cols) +   facet_wrap(~Species) + theme_bw()
}
totalbag = unique(full[, .(TotalBag,Species, Type)])
#Huntingbag fits were: Greylag `r GLBagOverlap` and Pinkfoot `r PFBagOverlap`

#```{r totalbag, echo=FALSE}
#totalbag
#```
```

```{r WingSurvey, eval=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}
simbag = fread('c:/MSV/WorkDirectory/HuntingBagRecord.txt')
simbag[, Species:=sapply(GameType, ConvertGameType)]
simbag[, Date:=as.IDate(as.Date(Day, origin = '1991-01-01'))]
simbag[, MDay:=data.table::mday(Date)]
simbag[MDay <= 14, Fortnight:=paste(data.table::month(Date),'I', sep = '-')]
simbag[MDay > 14, Fortnight:=paste(data.table::month(Date),'II', sep = '-')]
simbag[Day == 31, Fortnight:='1-II']  # Fix issue where day 31 gets month = 2
simbag[, Wings:=.N, by = c('Fortnight', 'Species')]
sorting = c("9-I", "9-II", "10-I","10-II", "11-I","11-II", "12-I","12-II", "1-I", "1-II")
simbag[, Fortnight:=factor(Fortnight, levels = sorting)]
tmp = unique(simbag[, .(Wings, Fortnight, Species)])
tmp[, PropBag:=Wings/sum(Wings), by = Species]
setnames(tmp, 'Species', 'Art')
tmp[, Art:=as.factor(Art)]
levels(tmp$Art) = c('Grågås', 'Kortnæb')
ggplot(tmp) + geom_bar(aes(x = Fortnight, y=PropBag, fill = Art), position="dodge", stat = 'identity') + 
	ylab('Andel af udbytte') + 
  xlab('Halvmåned')+
	scale_fill_viridis(discrete=TRUE) + 
	theme_bw()

```

## Functional responses
```{r functional, fig.height=6, fig.width=10, echo=FALSE}
invisible({
# Maize:
IntakeBN = fread(paste0(resultpath,'CurvePointsKJIntakeAtDiffMaizeDensitiesHoll_BN.txt'))
IntakeBN = IntakeBN[V1 <= 1000,]
IntakeBN[, Species:='Barnacle']
IntakeBN[, V2:=V2*0.87]
IntakePF = copy(IntakeBN)
IntakePF = IntakePF[, V2:=V2*1.26582]
IntakePF[, Species:='Pinkfeet']
IntakeGL = copy(IntakeBN)
IntakeGL = IntakeGL[, V2:=V2*1.46835]
IntakeGL[, Species:='Greylag']

maize = rbind(rbind(IntakeBN, IntakePF), IntakeGL)
maize[, Response:='Maize']
p = ggplot(maize, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab(expression(paste('kJ/', m^2))) + ylab('kJ per min')
# p = p + annotate('point', x = 119.1825 * 17.022, y =  26.77176744)
# p = p + annotate('point', x = 52.97 * 17.022, y =  18.50017869)
# p = p + annotate('point', x = 66.2125 * 17.022, y =  22.83291392)
p = p + ggtitle('Maize')

# Grain:
IntakePF = fread(paste0(resultpath, 'CurvePointsKJIntakeAtDiffGrainDensitiesHollNolet_PF.txt'))
IntakePF = IntakePF[V1 <= 2500,]
IntakePF[, Species:='Pinkfeet']
IntakePF[, V2:=V2 * 17.67 * 0.695 * 60]
IntakeBN = copy(IntakePF)
IntakeBN = IntakeBN[, V2:=V2*.79]
IntakeBN[, Species:='Barnacle']
IntakeGL= copy(IntakePF)
IntakeGL= IntakeGL[, V2:=V2*1.16]
IntakeGL[, Species:='Greylag']

grain = rbind(rbind(IntakeBN, IntakePF), IntakeGL)
grain[, Response:='Grain']
q = ggplot(grain, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab(expression(paste('Grain/', m^2))) + ylab('kJ per min')
q = q + ggtitle('Grain')

# Grass
GrassGL = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_GL.txt'))
GrassPF = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_PF.txt'))
GrassBN = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_BG.txt'))
GrassGL[, Species:='Greylag']
GrassBN[, Species:='Barnacle']
GrassPF[, Species:='Pinkfeet']

grass = rbind(rbind(GrassBN, GrassPF), GrassGL)
grass[, Response:='Grass']

z = ggplot(grass, aes(V1, V2, colour = Species)) + geom_line(size = .5) + theme_bw() + xlab('Grass height (cm)') + ylab('kJ per min')
z = z + ggtitle('Grass')

# Feeding time
interf = fread(paste0(resultpath, 'CurvePointsFeedingTimePettifor_PF.txt'))
interf = ggplot(interf, aes(V1, V2)) + geom_line(size = 1) + theme_bw() + xlab('Flock size') + ylab('Feeding time')
interf = interf + ggtitle('Feeding time')

responses = rbind(grain, maize)
# png(filename = 'o:/ST_GooseProject/ALMaSS/ODDoxImages/FunctionalResponseGrainMaize_2.png', height = 480/2, width = (480*2.5)/2, res =100)
# ggplot(responses, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab('kJ per m2') + ylab('kJ per min') + 
# facet_wrap(~Response, scales = 'free_x', nrow = 1)
# dev.off()
})
 grid.arrange(z, interf, p, q, nrow = 2, ncol = 2)
# png(filename = 'o:/ST_GooseProject/ALMaSS/ODDoxImages/FunctionalResponseGrass_2.png', height = 480/2, width = (480*1.5)/2, res = 100)
# z
# dev.off()
#jpeg(filename = 'o:/ST_Lada/Projekter/GBB/Figures/Interference.jpg', height = 480*4, width = 480*4, res = 400)
# interf
#dev.off()
# ggslackr(interf)
```


## Weather data
```{r weather, echo=FALSE, fig.width=10}
PlotWeather(file = file.path(resultpath, 'Vejlerne2009-2014.pre'), from = '2009-09-01', to = '2010-03-01')
```

## Configs
```{r config, echo=FALSE}
ScipenDefault = getOption('scipen')  # In case it should be turned back again.
options(scipen = 99)  # To avoid scientific notation in the resulting file
configs = fread(paste(resultpath, 'GooseConfig.txt', sep = ''))
kable(configs, caption = 'Config settings used in this run')
```

