---
title: "Goose model testing"
author: "The awesome Goose management Team"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, cache=FALSE, tidy=FALSE,echo=FALSE}
assign("depthtrigger", 60, data.table:::.global)  # To prevent data.table printing when removing columns. See: http://stackoverflow.com/questions/15267018/knitr-gets-tricked-by-data-table-assignment
```


```{r load, echo=FALSE,message=FALSE, warning=FALSE, include=FALSE}
# library(devtools)
# install_github('LDalby/ralmass')
packs = c('xtable', 'RColorBrewer', 'ralmass', 'gridExtra', 'knitr', 'lubridate', 'viridis', 'tidyverse',
          'data.table', 'stringr', 'readxl', 'ggvis', "sf", "raster", "ggmap", "broom", "maptools", "ggthemes")
sapply(packs, FUN = require, character.only = TRUE)
sysinfo <- Sys.info()
if ("Linux" == sysinfo[match("sysname", names(sysinfo))]) {
  resultpath <- '~/ALMaSS/WorkDirectory/'
  o_drive <- "/run/user/1000/gvfs/smb-share:server=uni.au.dk,share=dfs/ST_GooseProject/"
  git_dir <- "~/git/"
}
if ("Windows" == sysinfo[match("sysname", names(sysinfo))]) {
  resultpath <- 'c:/MSV/WorkDirectory/'
  o_drive <- "o:/ST_GooseProject/"
}
runinfo = readLines(file.path(resultpath, 'BatchALMaSS.ini'))
simyears = as.numeric(runinfo[length(runinfo) - 1])

extention = ''
sim = ''
extention = '.res'

```

This is a workdocument for collecting output from the **ALMaSS** Goose management model.

Document compiled: `r Sys.time()`

Number of simulation years: `r simyears` (only valid for commandline runs)

Results read from: `r resultpath`

Date stamp on ALMaSS exe file: `r file.info(paste0(resultpath, 'ALMaSS_CmdLine.exe'))$mtime` 

## Notes to run
`r Sys.Date()`. Things modified:

+ See the config table below for the settings used for the goose model. 
+ Testing different curves - see config table for settings



## Available forage
```{r forage, echo=FALSE, fig.width=14, fig.height=16, warning=FALSE}
coltypes = "iiiiiiiiiiiidddddcddicc"
forage <- read_tsv(file.path(resultpath, 'GooseFieldForageData.txt'), col_types = coltypes) %>% 
  mutate(Day = Day - 365, Date = as.Date(Day, origin = as.Date('2009-01-01'))) %>% 
  filter(month(Date) %in% c(8:12,1:3), Geese > 0) %>% 
  ClassifyHabitatUse(species = 'goose', timed = TRUE)

# First melt the numbers:
numbers_tb = forage %>%
  dplyr::select(Day, Polyref, Grain, Maize, Barnacle, Pinkfoot, Greylag) %>% 
  gather_(key_col = "Species", value_col = "Number", gather_cols = c("Barnacle", "Pinkfoot", "Greylag"))
  
# Then melt the grass forage
grassforage_tb = forage %>%
  dplyr::select(Day, Polyref, GrassPinkfoot, GrassBarnacle, GrassGreylag) %>% 
  gather_(key_col = "Species", value_col = "KjAvailable", gather_cols = c("GrassPinkfoot", "GrassBarnacle", "GrassGreylag")) %>% 
  mutate(Species = str_sub(Species, start = 6))

# Then merge and plot
left_join(numbers_tb, grassforage_tb, by = c('Day', 'Polyref', 'Species')) %>% 
  rename(Grass = KjAvailable) %>% 
  gather_(key_col = "Type", value_col = "KjAvailable", gather_cols = c('Grain', 'Maize', 'Grass')) %>% 
  filter(Number > 0, KjAvailable > 0.01) %>% 
  ggplot(aes(Day, KjAvailable)) + geom_point(alpha = 1/10, aes(size = log10(Number))) +
  facet_grid(Type~Species, scales = 'free_y') + theme_bw()
```
Plot characters and lines all have the same grey color, so black chunks are the result of overplotting. Only fields where the geese where actually foraging on are plotted. Dots are scaled to the logarithm of the numbers present on a field.
Turn off this chunk to save time when the document complies.

```{r mean_grain, echo=FALSE, fig.width=10, message=FALSE, warning=FALSE, eval=FALSE}
forage %>%
  filter(Grain > 0.0) %>% 
    mutate(grain_kj_pf = map_dbl(Grain, .f = get_func_resp, species = "Pinkfoot", resp = resp),
         grain_kj_gl = map_dbl(Grain, .f = get_func_resp, species = "Greylag", resp = resp),
         grain_kj_bn = map_dbl(Grain, .f = get_func_resp, species = "Barnacle", resp = resp)) %>% 
  dplyr::select(Season, Day, starts_with("grain_")) %>% 
  group_by(Season, Day) %>% 
  summarise(avg_kj_pf = mean(grain_kj_pf),
            avg_kj_gl = mean(grain_kj_gl),
            avg_kj_bn = mean(grain_kj_bn)) %>% 
  tidyr::gather(type, kJ, -Day, -Season) %>% 
    ggplot(aes(Day, kJ)) +
    geom_line(aes(color = type)) + 
    geom_point(aes(color = type)) +
    scale_color_colorblind() + 
    facet_wrap(~Season) +
    theme_bw() + 
    ggtitle("Mean daily kJ available from grain",
            subtitle = "kJ before flock size dependent feeding time adjustment \nOnly fields with geese")
```

## Weight development
```{r weight, echo=FALSE, fig.width=10, message=FALSE, warning=FALSE}
weights = fread(file.path(resultpath, 'GooseWeightStats.txt'), showProgress = FALSE) %>% 
    filter(MeanWeight != -1) %>% 
    mutate(Day = Day - 365,
           Date = as.Date(Day, origin = as.Date('2009-01-01')),
           SEupper = MeanWeight + StdError,
           SElower = MeanWeight - StdError)

weights %>% ggplot(aes(Date, MeanWeight)) +
      geom_point() +
      geom_errorbar(aes(ymin = SElower, ymax = SEupper), width = 0.5) + 
      facet_wrap(~Species, scales = 'free_y')
if ("Linux" == sysinfo[match("sysname", names(sysinfo))]) {
  col_types <- "Dcid"
  field <- read_tsv(file.path(git_dir,  '/ALMaSS_inputs/GooseManagement/Vejlerne/APIdata.txt'),
                    col_types = "Dcdd")
}
if ("Windows" == sysinfo[match("sysname", names(sysinfo))]) {
  field = fread('C:/MSV/ALMaSS_inputs/GooseManagement/Vejlerne/APIdata.txt')
}              
fits = CalcWeightFit(weights, field, measure = 'LS')
```

Fit(s) were `r fits`.

## Distance flown
```{r flightdistance, echo=FALSE, fig.height=6, fig.width=10}
massdropcols = c("BodyCondition", "MinForageRate")
energy <- fread(file.path(resultpath, 'GooseEnergeticsData.txt'), showProgress = FALSE, drop = massdropcols) %>% 
  as.tibble() %>% 
  mutate(Day = Day - 365,
         Date = as.Date(Day, origin = as.Date('2009-01-01'))) %>% 
  group_by(Day, GooseType) %>% 
  mutate(MeanDist = mean(FlightDistance)/1000)
energy %>% dplyr::select(Day, Date, GooseType, MeanDist, Season) %>% 
  distinct(.keep_all = TRUE) %>% 
  ggplot(aes(Date, MeanDist)) +
    geom_line(aes(color = GooseType)) +
    ylab('Mean distance flown per day (km)') +
    scale_color_brewer(palette = 'Paired') +
    scale_x_date(date_breaks = "1 month", date_labels = "%b") + 
    facet_wrap(~Season, scales = 'free_x')
```

## Full time
```{r fulltime, echo=FALSE, fig.height=5, fig.width=10}
energy %>% ggplot( aes(Day, FullTime)) +
  geom_hex(show.legend = TRUE) +
  scale_fill_viridis() +
  facet_grid(~GooseType)
```


## Number of flocks per day

```{r flocknumbers, echo=FALSE, fig.width=10}
forage %>%
  dplyr::select(Day, GreylagTimed, BarnacleTimed, PinkfootTimed, Season) %>%
  gather_(value_col = 'Numbers', key_col = 'Species', gather_cols = c("GreylagTimed", "BarnacleTimed", "PinkfootTimed")) %>%
  filter(Numbers > 0) %>%
  group_by(Day, Species) %>%
  mutate(N = n()) %>% 
  # filter(Day == 300 & Species == "PinkfootTimed")
  # write_delim(path = "o:/ST_GooseProject/ALMaSS/GooseParameterFitting/flock_sizes_1.txt")
  ggplot(aes(Day, N)) +
  geom_line() +
  facet_wrap(~Species, scales = 'free') +
  ylab('Flock numbers')
```

## AOR grid
```{r AOR_grid, echo=FALSE, fig.height=6, fig.width=10, message=FALSE}
# Define projection:
utm32 <- "+proj=utm +zone=32 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
# Define AOR grid size
grid_size = 1000
ext <- readShapePoly(file.path(o_drive, "/ALMaSS/GooseModelTesting/vejlerne_outline.shp"),
                     proj4string = CRS("+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs")) %>% 
  # spTransform(CRSobj = CRS(utm32)) %>% 
  extent()
# Define template raster
r1 <- raster(nrows = 24000/grid_size, 
             ncols = 36000/grid_size,
             ext = ext,
             crs = "+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs")
# Get the default value for FL  
cfg <- readLines(file.path(resultpath, 'TIALMaSSConfig.cfg'))
defaultval = GetParamValue(param = "GOOSE_FOLLOWINGLIKELYHOOD_PF",
                           config = cfg)
# Make spatial object of xy dump file
polygons <- read_tsv(file.path(resultpath, "GooseXYDump.txt"), col_types = "iiiiii") %>% 
  UtmToALMaSS(long = "X", lat = "Y", toalmass = FALSE, map = "VejlerneBigMap") %>% 
  dplyr::select(ALong, ALat) %>% 
  SpatialPoints(proj4string = CRS("+proj=utm +zone=32 +ellps=GRS80 +units=m +no_defs")) %>% 
  # Tally occurences in cells and plot
  rasterize(y = r1, fun = "count") %>% 
  # plot()
  rasterToPolygons() %>% 
  # st_as_sf() %>% 
  # st_transform(crs = "+init=epsg:4326") %>% 
  # ggplot() +
  #   geom_sf(aes(fill = layer)) +
  #   ylim(56.935, 57.15) +
  #   xlim(8.73, 9.35) +
  #   ggtitle("Grid cell occupancy - Pinkfoot",
  #           sub = paste0("Grid size = 1000m. Followinglikelyhood ", defaultval))
  spTransform(CRSobj = CRS("+init=epsg:4326"))
# Get a map background
# fields <- readShapePoly("C:/Users/lada/Git/shiny/vejlerne/Data/fields.shp",
#                         proj4string = CRS("+proj=longlat +datum=WGS84 +no_defs")) %>% 
#   spTransform(CRSobj = CRS("+init=epsg:4326")) %>% 

  
map <- st_read(dsn = file.path(o_drive, "ALMaSS/GooseModelTesting"), layer = "vejlerne_outline") %>% 
  st_transform(crs = "+init=epsg:4326") %>% 
  st_bbox() %>% 
  as.numeric() %>% 
  get_stamenmap(zoom = 11, maptype = "toner-lite")
# Ugly hack to make the plot work. Will be much nicer when geom_sf is fully implemented
# tmp <- tidy(fields)
tmp <- tidy(polygons)
tmp2 <- polygons@data
tmp2$id <- row.names(tmp2)
tmp3 <- left_join(tmp, tmp2)
# pdf(file = "C:/Users/lada/test.pdf")
ggmap(map) + 
  geom_polygon(data = tmp3, aes(long, lat, group = id, fill = layer)) + 
  scale_fill_gradient(guide = guide_legend(title = "Count")) +
  ggtitle("Grid cell occupancy - Pinkfeet",
          sub = paste0("Grid size = ", grid_size, "m. Followinglikelyhood ", defaultval))
# dev.off()

  
```

## AOR table - WIP
```{r AOR_table, echo=FALSE, message=FALSE, eval=FALSE}
aor_tab <- read_tsv(file.path(resultpath, "AORPinkfeet.txt"))
```


## Numbers
```{r numbers, echo=FALSE, fig.height=6, fig.width=10}
col_types <- "iiiiiiii"
read_tsv(file.path(resultpath, 'GoosePopulationData.txt'),
                 col_types = col_types) %>% 
  dplyr::mutate(Day = Day - 365) %>% 
  PlotGoosePopulation()
```
\newpage

## Leave reason
```{r leavereason, echo=FALSE, fig.height=8, fig.width=10}
leavereason <- read_tsv(file.path(resultpath, 'GooseLeaveReasonStats.txt'), col_types = "iiicci") %>% 
  filter(N > 0) %>% 
  mutate(Day = Day - 365)
if (nrow(leavereason) > 0) {
  ggplot(leavereason, aes(Day, N)) + 
    geom_line(aes(color = LeaveReason)) + 
    facet_grid(LeaveReason~SpeciesType, scales = 'free_y')
}
```

## Flock sizes
```{r flocks, echo=FALSE, fig.height=8, fig.width=10}
flocks <- read_csv(file.path(o_drive, '/Field data/Fugledata/fugledata_20150320_obs_clean.csv'),
                   col_types = "iiicc") %>% 
  filter(Month %in% c(9:12,1:3) & Hour >= 11 & Hour <= 13) %>% 
  dplyr::select(-Month, -Hour)

# Simulated data - max number on day
dists <- forage %>% 
  dplyr::select(Day, Barnacle, Pinkfoot, Greylag) %>% 
  mutate(ObsDato = as.Date(Day, origin = '2014-01-01')) %>% 
  filter(month(ObsDato) %in% c(9:12,1:3)) %>% 
  dplyr::select(-Day) %>% 
  gather_(key_col = 'Species', value_col = 'Numbers', gather_cols = c("Barnacle", "Pinkfoot", "Greylag")) %>% 
  filter(Numbers != 0) %>% 
  dplyr::select(-ObsDato) %>% 
  mutate(Type = "Simulated") %>% 
  bind_rows(flocks) %>% 
  mutate(Numbers = log10(Numbers), Count = "DailyMax")

DegreeOverlapB = round(CalcOverlap(dists, species = 'Barnacle', metric = 'Numbers'), digits = 2)
DegreeOverlapP = round(CalcOverlap(dists, species = 'Pinkfoot', metric = 'Numbers'), digits = 2)
DegreeOverlapG = round(CalcOverlap(dists, species = 'Greylag', metric = 'Numbers'), digits = 2)

# Timed counts:
dists1 <- forage %>% 
  dplyr::select(Day, BarnacleTimed, PinkfootTimed, GreylagTimed) %>% 
  mutate(ObsDato = as.Date(Day, origin = '2014-01-01')) %>% 
  filter(month(ObsDato) %in% c(9:12,1:3)) %>% 
  dplyr::select(-Day) %>% 
  gather_(key_col = 'Species', value_col = 'Numbers', gather_cols = c("BarnacleTimed", "PinkfootTimed", "GreylagTimed")) %>% 
  filter(Numbers != 0) %>% 
  dplyr::select(-ObsDato) %>% 
  mutate(Type = "Simulated") %>% 
  mutate(Species = recode(Species, 
                          "BarnacleTimed" = "Barnacle",
                          "PinkfootTimed" = "Pinkfoot",
                          "GreylagTimed" = "Greylag")) %>% 
  bind_rows(flocks) %>% 
  mutate(Numbers = log10(Numbers), Count = "Timed")

DegreeOverlapBT = round(CalcOverlap(dists1, species = 'Barnacle', metric = 'Numbers'), digits = 2)
DegreeOverlapPT = round(CalcOverlap(dists1, species = 'Pinkfoot', metric = 'Numbers'), digits = 2)
DegreeOverlapGT = round(CalcOverlap(dists1, species = 'Greylag', metric = 'Numbers'), digits = 2)

bind_rows(dists, dists1) %>% 
  ggplot(aes(x = Numbers, fill = Type)) +
  geom_density(alpha = 0.5, colour = NA) +
  facet_grid(Count ~ Species, scales = 'free_x') +
  theme_bw()
```

The degree of overlap is: Barnacle `r DegreeOverlapB`, Pinkfoot `r DegreeOverlapP`, & Greylag `r DegreeOverlapG`. For the timed counts the degree of overlap is: Barnacle `r DegreeOverlapBT`, Pinkfoot `r DegreeOverlapPT`, & Greylag `r DegreeOverlapGT`.

## Distance from foraging sites to nearest roost
```{r distances, echo=FALSE, fig.height=6, fig.width=12, message=FALSE}
# Data was handled here:
# Load function that was previous part of the ralmass package:
# source("~/git/almass/calc_pseudo_centroid.r")
# # Define function to convert ArtID to chr species names:
# num_id_to_chr = function(id) {
# 	switch(EXPR = as.character(id),
# 		'63' = 'Pinkfoot',
# 		'59' = 'Greylag',
# 		'67' = 'Barnacle',
# 		'Undefined species')
# }
# 
# polys <- read_excel(file.path(o_drive, 'Field data/Fugledata_Obslist_20160414_clean.xlsx'), sheet = 'Polygon') %>%
#   dplyr::select(PolyID, PolygonData) %>%
#   CalcPseudoCentroid(project = TRUE) %>%
#   UtmToALMaSS(long = 'UtmX', lat = 'UtmY', map = 'VejlerneBigMap', subset = TRUE) %>%
#   dplyr::select(PolyID, X = ALong, Y = ALat)
# 
# library(lubridate)
# 
# obs <- read_excel(file.path(o_drive, 'Field data/Fugledata_Obslist_20160414_clean.xlsx'), sheet = 'Observation') %>%
#   dplyr::filter(Year == 2015, Month %in% c(9,10,11,12,1,2,3), ArtID %in% c(63, 59, 67)) %>%
#   mutate(Species = map_chr(.x = ArtID, .f = num_id_to_chr),
#          Date = lubridate::ymd_hms(ObsDato),
#          Week = lubridate::week(Date)) %>%
#   dplyr::select(PolygonID, Date, Week, Species, Antal)
# 
# # Construct path to field data on the o-drive:
# pth <- file.path(o_drive, paste0("Field data/FieldobsDistancesFromRoost", Sys.Date(), ".txt"))
# 
# inner_join(polys, obs, by = c("PolyID" = "PolygonID")) %>%
#   mutate(dist = pmap_dbl(list(X, Y, Species), .f = find_closest)) %>%
#   data.table::fwrite(file = pth, quote = FALSE, sep = "\t")

# Get the field centroids from the polyref file
poly <- read_tsv(file.path(resultpath, "VejlerneOpenMay2016PolyRef.txt"),
                 skip = 1,
                 col_types = "iiiiiiiii") %>% 
  dplyr::select(PolyRefNum, CentroidX, CentroidY)
# Read in the precalculated distance from the field data
col_types_field <- "dddTicdd"
fieldobs <- read_tsv(file.path(o_drive, 'Field data/FieldobsDistancesFromRoost2017-08-01.txt'),
                     col_types = col_types_field) %>% 
    mutate(week = ifelse(Week < 25, Week + 55, Week), 
         # Season = 1,
         Type = "Fieldobs")

fieldobs_weekly <- fieldobs %>% 
  group_by(week, Species, Type) %>% 
  summarise(mean_dist = mean(dist))

# Calculate distances from the simulation
forage_dist <- forage %>% 
  dplyr::select(Season, Date, Polyref, Barnacle, Pinkfoot, Greylag) %>%
  gather_(value_col = "Numbers", key_col = "Species", gather_cols = c("Barnacle", "Pinkfoot", "Greylag")) %>%
  # select(Season, Day, Polyref, ends_with("Timed")) %>%
  # gather_(value_col = "Numbers", key_col = "Species", gather_cols = paste0(c("Barnacle", "Pinkfoot", "Greylag"), "Timed")) %>%
  filter(Numbers > 0) %>% 
  mutate(week = lubridate::week(Date)) %>% 
  mutate(week = if_else(week < 25, week + 55, week)) %>% 
  left_join(poly, by = c("Polyref" = "PolyRefNum")) %>% 
  mutate(dist = pmap_dbl(list(CentroidX, CentroidY, Species), .f = find_closest),
         Type = "Simulated")

sim_weekly <- forage_dist %>%   
  group_by(week, Species, Type) %>% 
  dplyr::summarise(mean_dist = mean(dist))

# Make a combined plot: 
bind_rows(sim_weekly, fieldobs_weekly) %>% 
  ggplot(aes(week, mean_dist/1000)) + 
  geom_line(aes(color = Species, linetype = Type)) + 
  ggtitle("Mean weekly distance (km) from forage location to roost", subtitle = "Simulated data is averaged over five seasons. Field observations are from 2015.") +
  scale_color_colorblind() + 
  scale_x_continuous(breaks = seq(35, 75, by = 5), 
                     limits = c(35, 70),
                     labels = as.character(c(seq(35, 55, by = 5), c(5,10, 15, 20)))) + 
  scale_y_continuous(limits = c(0, 11), breaks = seq(0,11,2)) +
  theme_fivethirtyeight() + 
  theme(axis.text = element_text(size = 12))
  
# Calculate fit
# First join the data
distances <- dplyr::inner_join(sim_weekly, fieldobs_weekly,
                  by = c("week", "Species"), 
                  suffix = c("_sim", "_fieldobs")) %>% 
  dplyr::group_by(Species) %>% 
  dplyr::mutate(min_dist = min(c(mean_dist_sim, mean_dist_fieldobs)),
                max_dist = max(c(mean_dist_sim, mean_dist_fieldobs)),
                scaled_sim = (mean_dist_sim - min_dist) / (max_dist - min_dist),
                scaled_field = (mean_dist_fieldobs - min_dist) / (max_dist - min_dist))
distance_fits <- distances %>%  
  dplyr::summarise(ls = sum((scaled_field - scaled_sim)^2))

distfit_bn <- distance_fits %>% filter(Species == "Barnacle") %>% pull(ls)
distfit_gl <- distance_fits %>% filter(Species == "Greylag") %>% pull(ls)
distfit_pf <- distance_fits %>% filter(Species == "Pinkfoot") %>% pull(ls)
``` 
The degree of overlap is: Barnacle `r distfit_bn`, Pinkfoot `r distfit_pf`, & Greylag `r distfit_gl`.


## Habitat use
```{r habitat, habitatuse, echo=FALSE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE}
field_data <- read_csv(file.path(o_drive, 'Field data/Fugledata/HabitatUseAll2014.csv'),
                      col_types = "icic") %>% 
  dplyr::mutate(habitat_use = recode(HabitatUse,
                             "Stubble undersown" = "Stubble",
                             "UnharvestedBarley" = "Stubble"),
         Month = ifelse(Month < 7, Month + 12, Month)) %>% 
  dplyr::filter(HabitatUse != "Plowed") %>% 
  dplyr::group_by(Month, Species, habitat_use) %>% 
  dplyr::mutate(numbers = sum(N)) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::select(-N, -HabitatUse) %>% 
  dplyr::distinct() %>% # needed this one after some categories were joined
  dplyr::group_by(Month, Species) %>%  # need this to avoid grouping by habitat_use here
  dplyr::mutate(prop_field = numbers/sum(numbers)) %>% 
  dplyr::rename(month = Month,
                species = Species)
    
cols <- c("Grass" = "#66C2A5",
          "Maize" = "#FC8D62",
          "Rape" = "#8DA0CB",
          "Stubble" = "#E78AC3",
          "WinterCereal" = "#A6D854")

fd_plot <- field_data %>% 
  ggplot(aes(month, fill = habitat_use)) +
  geom_bar(aes(weight = numbers), position = 'fill') + 
  facet_wrap(~species, scales = "free_x") + 
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  scale_y_continuous(labels = scales::percent) + 
  ylab("Use") + 
  scale_x_continuous(breaks = 9:13, 
                     labels = c("9", "10", "11", "12", "1"),
                     limits = c(8, 14)) +
  theme_fivethirtyeight() +
  ggtitle("Field data habitat use")
  

forage <- forage %>% 
  mutate(month = month(Date),
         month = ifelse(month < 6, month + 12, month))
# Strp the relevant columns and construct a habitat use data set
habpf <- forage %>% 
  dplyr::select(Season, month, habitat_use = HabitatUsePF, numbers = PinkfootTimed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(Season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "Pinkfoot",
                prop = numbers/sum(numbers))

habgl <- forage %>% 
  dplyr::select(Season, month, habitat_use = HabitatUseGL, numbers = GreylagTimed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(Season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "Greylag",
                prop = numbers/sum(numbers))

habbn <- forage %>% 
  dplyr::select(Season, month, habitat_use = HabitatUseBN, numbers = BarnacleTimed) %>% 
  dplyr::filter(numbers > 0) %>% 
  dplyr::group_by(Season, month, habitat_use) %>% 
  dplyr::summarise(numbers = sum(numbers)) %>% 
  dplyr::mutate(species = "Barnacle",
                prop = numbers/sum(numbers))

sim_data <- bind_rows(habpf, habgl, habbn)
  
# Combine this and plot  
s_plot <- sim_data %>% 
  ggplot(aes(month, fill = habitat_use)) +
  geom_bar(aes(weight = numbers), position = 'fill') + 
  facet_wrap(~species, scales = "free_x") + 
  scale_fill_manual(values = cols, guide_legend(title = "Habitat")) +
  scale_y_continuous(labels = scales::percent) + 
  ylab("Use") + 
  scale_x_continuous(breaks = 9:13,
                     labels = c("9", "10", "11", "12", "1"),
                     limits = c(8, 14)) +
  theme_fivethirtyeight() +
  ggtitle("Simulated habitat use")

grid.arrange(fd_plot, s_plot)

# Calculate the fit:
habitat_use_fits <- inner_join(sim_data, field_data,
          by = c("month", "habitat_use", "species")) %>% 
  replace_na(list(prop = 0.0)) %>% 
  dplyr::mutate(sq_diff = (prop - prop_field)^2) %>%
  dplyr::group_by(Season, month, species) %>% 
  dplyr::summarise(ls = sum(sq_diff)) %>% 
  dplyr::group_by(species) %>% 
  dplyr::summarise(avg_ls = mean(ls))

HabUsePF = habitat_use_fits %>% filter(species == "Pinkfoot") %>% pull(avg_ls)
HabUseGL = habitat_use_fits %>% filter(species == "Greylag") %>% pull(avg_ls)
HabUseBN = habitat_use_fits %>% filter(species == "Barnacle") %>% pull(avg_ls)
```
Habitat use fits were: Barnacle `r HabUseBN`, Greylag `r HabUseGL` & Pinkfoot `r HabUsePF`

## Huntingbag
```{r HuntingBag, eval=FALSE, fig.height=6, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
bag = fread('o:/ST_GooseProject/ALMaSS/HunterModelTesting/SurveyResults/THS_JAM_Goosehunters_2013.csv')
bag = bag[!is.na(ABMhunter),.(ABMhunter, Greylag, Pinkfeet)]
setnames(bag, old = 'Pinkfeet', new = 'Pinkfoot')
bag = melt(bag, id.vars = 'ABMhunter', measure.vars = c('Greylag', 'Pinkfoot'), variable.name = 'Species', value.name = 'NoShot')
bag[, Type:='Fieldobs']
	
simbag = fread('c:/MSV/WorkDirectory/HuntingBagRecord.txt')
if(nrow(simbag) != 0){ 
  simbag[, Species:=sapply(GameType, ConvertGameType)]
  simbag[, NoShot:=.N, by = c('Species', 'HunterRef')]
  sim = unique(simbag[, .(HunterRef, Species, NoShot)])
  sim[, Type:='Simulated']
  full = rbind(bag[NoShot != 0, .(Species, NoShot, Type)], sim[, .(Species, NoShot, Type)])
  full[, TotalBag:=sum(NoShot), by = c('Species', 'Type')]
  
  GLBagOverlap = CalcOverlap(data = full, species = 'Greylag', metric = 'NoShot')
  PFBagOverlap = CalcOverlap(data = full, species = 'Pinkfoot', metric = 'NoShot')

  cols = c('Fieldobs' = brewer.pal(8,'Dark2')[4], 'Simulated' = brewer.pal(8,'Dark2')[5])
  ggplot(full, aes(NoShot, fill = Type)) + geom_density(alpha = 0.5, colour = NA) + scale_fill_manual(values = cols) +   facet_wrap(~Species) + theme_bw()
}
totalbag = unique(full[, .(TotalBag,Species, Type)])
#Huntingbag fits were: Greylag `r GLBagOverlap` and Pinkfoot `r PFBagOverlap`

#```{r totalbag, echo=FALSE}
#totalbag
#```
```

```{r WingSurvey, eval=FALSE, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}
simbag = fread('c:/MSV/WorkDirectory/HuntingBagRecord.txt')
simbag[, Species:=sapply(GameType, ConvertGameType)]
simbag[, Date:=as.IDate(as.Date(Day, origin = '1991-01-01'))]
simbag[, MDay:=data.table::mday(Date)]
simbag[MDay <= 14, Fortnight:=paste(data.table::month(Date),'I', sep = '-')]
simbag[MDay > 14, Fortnight:=paste(data.table::month(Date),'II', sep = '-')]
simbag[Day == 31, Fortnight:='1-II']  # Fix issue where day 31 gets month = 2
simbag[, Wings:=.N, by = c('Fortnight', 'Species')]
sorting = c("9-I", "9-II", "10-I","10-II", "11-I","11-II", "12-I","12-II", "1-I", "1-II")
simbag[, Fortnight:=factor(Fortnight, levels = sorting)]
tmp = unique(simbag[, .(Wings, Fortnight, Species)])
tmp[, PropBag:=Wings/sum(Wings), by = Species]
setnames(tmp, 'Species', 'Art')
tmp[, Art:=as.factor(Art)]
levels(tmp$Art) = c('Gr?g?s', 'Kortn?b')
ggplot(tmp) + geom_bar(aes(x = Fortnight, y=PropBag, fill = Art), position="dodge", stat = 'identity') + 
	ylab('Andel af udbytte') + 
  xlab('Halvm?ned')+
	scale_fill_viridis(discrete=TRUE) + 
	theme_bw()

```

## Functional responses
```{r functional, fig.height=6, fig.width=10, echo=FALSE}
invisible({
# Maize:
IntakeBN = fread(paste0(resultpath,'CurvePointsKJIntakeAtDiffMaizeDensitiesHoll_BN.txt'))
IntakeBN = IntakeBN[V1 <= 1000,]
IntakeBN[, Species := 'Barnacle']
IntakeBN[, V2 := V2 * 0.87]
IntakePF = copy(IntakeBN)
IntakePF = IntakePF[, V2 := V2 * 1.26582]
IntakePF[, Species := 'Pinkfeet']
IntakeGL = copy(IntakeBN)
IntakeGL = IntakeGL[, V2 := V2 * 1.46835]
IntakeGL[, Species := 'Greylag']

maize = rbind(rbind(IntakeBN, IntakePF), IntakeGL)
maize[, Response := 'Maize']
p = ggplot(maize, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab(expression(paste('kJ/', m^2))) + ylab('kJ per min')
# p = p + annotate('point', x = 119.1825 * 17.022, y =  26.77176744)
# p = p + annotate('point', x = 52.97 * 17.022, y =  18.50017869)
# p = p + annotate('point', x = 66.2125 * 17.022, y =  22.83291392)
p = p + ggtitle('Maize')

# Grain:
IntakePF = fread(paste0(resultpath, 'CurvePointsKJIntakeAtDiffGrainDensitiesHollNolet_PF.txt'))
IntakePF = IntakePF[V1 <= 2500,]
IntakePF[, Species := 'Pinkfeet']
IntakePF[, V2 := V2 * 17.67 * 0.695 * 60]
IntakeBN = copy(IntakePF)
IntakeBN = IntakeBN[, V2 := V2 * .79]
IntakeBN[, Species := 'Barnacle']
IntakeGL = copy(IntakePF)
IntakeGL = IntakeGL[, V2 := V2 * 1.16]
IntakeGL[, Species := 'Greylag']

grain = rbind(rbind(IntakeBN, IntakePF), IntakeGL)
grain[, Response := 'Grain']
q = ggplot(grain, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab(expression(paste('Grain/', m^2))) + ylab('kJ per min')
q = q + ggtitle('Grain')

# Grass
GrassGL = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_GL.txt'))
GrassPF = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_PF.txt'))
GrassBN = fread(paste0(resultpath, 'CurvePointsKJIntakeAtVaryingGrassHeights_BG.txt'))
GrassGL[, Species := 'Greylag']
GrassBN[, Species := 'Barnacle']
GrassPF[, Species := 'Pinkfeet']

grass = rbind(rbind(GrassBN, GrassPF), GrassGL)
grass[, Response := 'Grass']

z = ggplot(grass, aes(V1, V2, colour = Species)) + geom_line(size = .5) + theme_bw() + xlab('Grass height (cm)') + ylab('kJ per min')
z = z + ggtitle('Grass')

# Feeding time
interf = fread(paste0(resultpath, 'CurvePointsFeedingTimePettifor_PF.txt'))
interf = ggplot(interf, aes(V1, V2)) + geom_line(size = 1) + theme_bw() + xlab('Flock size') + ylab('Feeding time')
interf = interf + ggtitle('Feeding time')

responses = rbind(grain, maize)
# png(filename = 'o:/ST_GooseProject/ALMaSS/ODDoxImages/FunctionalResponseGrainMaize_2.png', height = 480/2, width = (480*2.5)/2, res =100)
# ggplot(responses, aes(V1, V2, colour = Species)) + geom_line(size = 1) + theme_bw() + xlab('kJ per m2') + ylab('kJ per min') + 
# facet_wrap(~Response, scales = 'free_x', nrow = 1)
# dev.off()
})
 grid.arrange(z, interf, p, q, nrow = 2, ncol = 2)
# png(filename = 'o:/ST_GooseProject/ALMaSS/ODDoxImages/FunctionalResponseGrass_2.png', height = 480/2, width = (480*1.5)/2, res = 100)
# z
# dev.off()
#jpeg(filename = 'o:/ST_Lada/Projekter/GBB/Figures/Interference.jpg', height = 480*4, width = 480*4, res = 400)
# interf
#dev.off()
# ggslackr(interf)
```


## Weather data
```{r weather, echo=FALSE, fig.width=10}
PlotWeather(file = file.path(resultpath, 'Vejlerne2009-2014.pre'), from = '2009-09-01', to = '2010-03-01')
```

## Configs
```{r config, echo=FALSE}
ScipenDefault = getOption('scipen')  # In case it should be turned back again.
options(scipen = 99)  # To avoid scientific notation in the resulting file
if (file.exists(file.path(resultpath, "GooseConfig.txt"))) {
  configs = fread(file.path(resultpath, 'GooseConfig.txt'))
  kable(configs, caption = 'Config settings used in this run')
}

```

